---
title: "betaSandwich"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/jeksterslab/betaSandwich/workflows/R-CMD-check/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions)
[![test-coverage](https://github.com/jeksterslab/betaSandwich/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/test-coverage.yaml)
[![codecov](https://codecov.io/gh/jeksterslab/betaSandwich/branch/main/graph/badge.svg)](https://codecov.io/gh/jeksterslab/betaSandwich)
<!-- badges: end -->

## Description

Generates robust confidence intervals for standardized regression coefficients
using heteroscedasticity-consistent standard errors for models fitted by `lm()` as described in Dudgeon (2017: http://doi.org/10.1007/s11336-017-9563-z).

## Installation

You can install the released version of
`betaSandwich`
from
[GitHub](https://github.com/jeksterslab/betaSandwich) with:

```r
install.packages("remotes")
remotes::install_github("jeksterslab/betaSandwich")
```

## Documentation

See
[GitHub Pages](https://jeksterslab.github.io/betaSandwich/index.html)
for package documentation.

## Example

In this example, a multiple regression model is fitted
using the overall rating (`rating`) as the regressand/outcome variable
and the rest of the variables as regressor/predictor variables
using the `datasets::attitude` data set (Chatterjee & Price, 1977).
Robust confidence intervals for the standardized regression coefficients are generated
using the `BetaHC()` function from the `betaSandwich` package following Dudgeon (2017).

```{r}
#| message = FALSE
library(betaSandwich)
```

### Fit the regression model using the `lm()` function.

```{r}
object <- lm(rating ~ ., data = attitude)
```

### Estimate the standardized regression slopes and the corresponding robust sampling covariance matrix.

```{r}
BetaHC(object, type = "hc3")
```

### References

Dudgeon, P. (2017).
Some improvements in confidence intervals for standardized regression coefficients. 
*Psychometrika*, 82 (4), 928–951.
https://doi.org/10.1007/s11336-017-9563-z

Chatterjee, S. and Price, B. (1977).
*Regression Analysis by Example*.
New York: Wiley.
(Section 3.7, p.68ff of 2nd ed.(1991).) 
