---
title: "betaSandwich: Example Using the DiffBetaSandwich Function"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betaSandwich: Example Using the DiffBetaSandwich Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Confidence intervals for
differences of standardized regression slopes
are generated using
the `DiffBetaSandwich()` function from the `betaSandwich` package.
In this example,
we use the data set and the model used in
[betaSandwich: Example Using the BetaHC Function](example-beta-sandwich.html).

```{r}
#| message = FALSE
library(betaSandwich)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaSandwich"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaSandwich::nas1982
```

## Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

## Estimate the standardized regression slopes and the corresponding sampling covariance matrix.

#### Multivariate Normal-Theory Approach

```{r}
std_mvn <- BetaN(object)
```

#### Asymptotic Distribution-Free Approach

```{r}
std_adf <- BetaADF(object)
```

#### HC3

```{r}
std_hc3 <- BetaHC(object, type = "hc3")
```

## Estimate differences of standardized regression slopes and the corresponding sampling covariance matrix.

```{r}
mvn <- DiffBetaSandwich(std_mvn)
adf <- DiffBetaSandwich(std_adf)
hc3 <- DiffBetaSandwich(std_hc3)
```

## Methods

### summary

Summary of the results of `DiffBetaSandwich()`.

```{r}
summary(mvn)
summary(adf)
summary(hc3)
```

### coef

Calculate differences of standardized regression slopes.

```{r}
coef(mvn)
coef(adf)
coef(hc3)
```

### vcov

Calculate the sampling covariance matrix of differences of standardized regression slopes.

```{r}
vcov(mvn)
vcov(adf)
vcov(hc3)
```

### confint

Generate confidence intervals for differences of standardized regression slopes.

```{r}
confint(mvn, level = 0.95)
confint(adf, level = 0.95)
confint(hc3, level = 0.95)
```

## References

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.
