---
title: "betaSandwich: Example"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betaSandwich: Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example, a multiple regression model is fitted
using the overall rating (`rating`) as the regressand/outcome variable
and the rest of the variables as regressor/predictor variables
using the `datasets::attitude` data set (Chatterjee & Price, 1977).
Robust confidence intervals for the standardized regression coefficients are generated
using the `BetaHC()` function from the `betaSandwich` package following Dudgeon (2017).

```{r}
#| message = FALSE
library(betaSandwich)
```

## Fit the regression model using the `lm()` function.

```{r}
object <- lm(rating ~ ., data = attitude)
```

## Estimate the standardized regression slopes and the corresponding robust sampling covariance matrix.

```{r}
BetaHC(object, type = "hc3")
```

## Methods

```{r}
out <- BetaHC(object, type = "hc3")
```

### summary

Summary of the results of `BetaHC()`.

```{r}
summary(out)
```

### coef

Calculate the standardized regression slopes.

```{r}
coef(out)
```

### vcov

Calculate the robust sampling covariance matrix of the standardized regression slopes.

```{r}
vcov(out)
```

### confint

Generate robust confidence intervals for standardized regression slopes.

```{r}
confint(out, level = 0.95)
```

## References

Dudgeon, P. (2017).
Some improvements in confidence intervals for standardized regression coefficients. 
*Psychometrika*, 82 (4), 928–951.
https://doi.org/10.1007/s11336-017-9563-z

Chatterjee, S. and Price, B. (1977).
*Regression Analysis by Example*.
New York: Wiley.
(Section 3.7, p.68ff of 2nd ed.(1991).) 
