---
title: "betaSandwich"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
bibliography: "vignettes.bib"
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
nocite: |
  @Pesigan-Sun-Cheung-2023
  @Dudgeon-2017
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![CRAN Status](https://www.r-pkg.org/badges/version/betaSandwich)](https://cran.r-project.org/package=betaSandwich)
[![R-Universe Status](https://jeksterslab.r-universe.dev/badges/betaSandwich)](https://jeksterslab.r-universe.dev/betaSandwich)
[![DOI](https://zenodo.org/badge/DOI/10.1080/00273171.2023.2201277.svg)](https://doi.org/10.1080/00273171.2023.2201277)
[![Make Project](https://github.com/jeksterslab/betaSandwich/actions/workflows/make.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/make.yml)
[![R-CMD-check](https://github.com/jeksterslab/betaSandwich/actions/workflows/check-full.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/check-full.yml)
[![R Package Test Coverage](https://github.com/jeksterslab/betaSandwich/actions/workflows/test-coverage.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/test-coverage.yml)
[![Lint R Package](https://github.com/jeksterslab/betaSandwich/actions/workflows/lint.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/lint.yml)
[![Package Website (GitHub Pages)](https://github.com/jeksterslab/betaSandwich/actions/workflows/pkgdown-gh-pages.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/pkgdown-gh-pages.yml)
[![Compile LaTeX](https://github.com/jeksterslab/betaSandwich/actions/workflows/latex.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/latex.yml)
[![Shell Check](https://github.com/jeksterslab/betaSandwich/actions/workflows/shellcheck.yml/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/shellcheck.yml)
[![pages-build-deployment](https://github.com/jeksterslab/betaSandwich/actions/workflows/pages/pages-build-deployment/badge.svg)](https://github.com/jeksterslab/betaSandwich/actions/workflows/pages/pages-build-deployment)
[![codecov](https://codecov.io/gh/jeksterslab/betaSandwich/branch/main/graph/badge.svg?token=KVLUET3DJ6)](https://codecov.io/gh/jeksterslab/betaSandwich)
<!-- badges: end -->

## Description

Generates robust confidence intervals for standardized regression coefficients
using heteroskedasticity-consistent standard errors for models fitted by `lm()`
as described in Dudgeon (2017: http://doi.org/10.1007/s11336-017-9563-z).
The package can also be used to generate confidence intervals for R-squared,
adjusted R-squared, and differences of standardized regression coefficients.
A description of the package and code examples
are presented in Pesigan, Sun, and Cheung (2023: https://doi.org/10.1080/00273171.2023.2201277).

## Installation

You can install the CRAN release of `betaSandwich` with:

```r
install.packages("betaSandwich")
```

You can install the development version of `betaSandwich` from
[GitHub](https://github.com/jeksterslab/betaSandwich) with:

```r
if (!require("remotes")) install.packages("remotes")
remotes::install_github("jeksterslab/betaSandwich")
```

## Example

In this example, a multiple regression model is fitted
using program quality ratings (`QUALITY`) as the regressand/outcome variable
and number of published articles attributed to the program faculty members (`NARTIC`),
percent of faculty members holding research grants (`PCTGRT`), and
percentage of program graduates who received support (`PCTSUPP`) as regressor/predictor variables
using a data set from 1982 ratings of 46 doctoral programs in psychology in the USA [@NationalResearchCouncil-1982].
Robust confidence intervals for the standardized regression coefficients are generated
using the `BetaHC()` function from the `betaSandwich` package following @Dudgeon-2017.

```{r}
#| message = FALSE
library(betaSandwich)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaSandwich"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
df <- betaSandwich::nas1982
```

### Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

### Estimate the standardized regression slopes and the corresponding robust sampling covariance matrix.

```{r}
BetaHC(object, type = "hc3", alpha = 0.05)
```

## Other Features

The package can also be used to generate confidence intervals for
R-squared,
adjusted R-squared,
and
differences of standardized regression coefficients.

## Documentation

See
[GitHub Pages](https://jeksterslab.github.io/betaSandwich/index.html)
for package documentation.

## Citation

To cite `betaSandwich` in publications, please cite @Pesigan-Sun-Cheung-2023.

## References
